\chapter{Introduction}
\pagenumbering{arabic}\hspace{3mm}

Speech recognition - the process of recognizing human speech and converting it to text, has emerged as a new trending technology in the IT industry. Mobile users desire devices that they can control without much physical interaction. Applications like Cortana are steadily gaining popularity with their hands free features like taking reminders and notes, opening other applications, and their witty replies. With the advancement in network capabilities, these applications can send data over to the servers where sophisticated algorithms provide exceptionally accurate recognition results. However, in countries like India where over 75 percent of the population has no internet, these applications are not apt. Moreover, privacy is a big issue as these systems share the voice data with third party servers.

In this work, we aim to implement a portable word based embedded speech recognition system for mobile phones, along with a graphics user interface for training on desktop, and a demonstrative voice controlled assistant for android. In chapter \ref{ch:survey}, we discuss a few related works and technologies of the proposed system. In chapter \ref{ch:proposal} we present the design and implementation of the proposed systems. In chapter \ref{ch:experiment} we discuss the expermients performed and their observations. Finally, we draw out conclusions and discuss the future work in chapter \ref{ch:conclusion}. In the appendix, we provide details of the assumed knowledge.